---
title: "TEST2"
author: "Yuan Yuan"
```{r}
#load data 
aburl = 'http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data'#initial aburl as the data from the website
abnames = c('sex','length','diameter','height','weight.w','weight.s','weight.v','weight.sh','rings')#initial abanames as different variables
abalone = read.table(aburl, header = F , sep = ',',  col.names = abnames)
#define column name and use the names we defined above
```

Problem 1
```{r}
#choose the column, weight.w, in the dataframe and calculate min,max,mean and var based on the given information. Then, putting results into a dataframe, rename the rows and columns, and outputting the dataframe.
Whole_wgt_sample<-function(my_data,x,total_num){ #define a function called Whole_wgt_sample with inputs: my_data, x and total_num inputs. my_data is the data we use, x is the samplesize and total_num is the total number of samples in my_data
  s<-my_data[sample(length(my_data), round(total_num*x), replace = FALSE)] #initial a variable to store selected samples from my_data with samplesize, x
  s_sum<-c(min(s),max(s),mean(s),var(s)) #initial a variable "s_sum"" to store the min, max, mean and variance of s 
  s_sum #output s_sum
} #finish the function
data_frame_1<-function(my_data){ #define a function data_frame_1 with input my_data 
  the_sample_size<-c(.01,.1,.25,.5,.8,1) #initial variable the_sample_size and put the percentage of the_sample_size we want in it 
  q1<-data.frame(Whole_wgt_sample(my_data,the_sample_size[1],length(my_data)),Whole_wgt_sample(my_data,the_sample_size[2],length(my_data)),Whole_wgt_sample(my_data,the_sample_size[3],length(my_data)),Whole_wgt_sample(my_data,the_sample_size[4],length(my_data)),Whole_wgt_sample(my_data,the_sample_size[5],length(my_data)),Whole_wgt_sample(my_data,the_sample_size[6],length(my_data))) #initial dataframe q1 and put the output of Whole_wgt_sample with 5 different kinds of sample sizes together into it
  rownames(q1)=c('SampleMin', 'SampleMax', 'SampleMean', 'SampleVar') #initial names for q1's rows
  colnames(q1)<-c('1%sample','10%sample','25%sample','50%sample','80%sample','100%sample') #initial names for q1's columns
  q1 #output dataframe q1
} #finish the function
data_frame_1(abalone$weight.w) #run the function data_frame_1 with abalone$weight.w data
```

Problem 2
```{r}
#This function will help to draw a well-organized histogram for the data we use. Then we create function grid_histogram_1 to draw a grid of histograms for each sample size by using par() and for loop function
histograms<-function(data_set,y){ #create a function histograms with input data_set and y, data_set is the data we use and y is the samplesize
  hist(data_set, #use hist() to draw hisgtogram for data_set 
      main=paste('Histogram with ',round(y*100),'% sample'), #initial the title for histogram
      xlab='variable') #initial the name for the xlab variable
}
grid_histogram_1<-function(my_data){ #define a function grid_histogram_1 with input my_data
  the_sample_size<-c(.01,.1,.25,.5,.8,1) #initial variable the_sample_size and put the percentage of samplesize into it 
  sample_number<-round(length(my_data)*the_sample_size) #intial the variable sample_number which is the number of samples taken for each samplesize
  par(mfrow=c(2,3)) #use par() to arrange the histogram in rows and columns with the parameters 2 and 3
  for (i in 1:(length(sample_number))){ #for loop
    s2<-c() #initial an empty variable s2, which is a temporary variable for drawing the histogram.
    s2<-my_data[sample(length(my_data),sample_number[i],replace = FALSE)] #define s2 as the samples selected from my_data
    histograms(s2,the_sample_size[i]) #use function histograms() to draw individual histogram for the certain samplesize
  }
}#finish the function
grid_histogram_1(abalone$weight.w) #run function grid_histogram_1() with abalone$weight.w
```

Problem 3
```{r}
#]we will define a function to take 1000 samples, store in dataframe, and calculate the means for every 1000 samples, then store in a variable
data_frame_2<-function(my_data){ #define a function data_frame_2() with input my_data
  the_sample_size<-c(.01,.1,.25,.5,.8,1) #initial variable samplesize and put the percentage of samplesize we want in it 
  a<-data.frame(c1=c(NA),c2=c(NA),c3=c(NA),c4=c(NA),c5=c(NA))#initial an empty dataframe a with 5 columns
  mean3<-c()#initial variable mean3 as empty
  for (i in 1:(length(the_sample_size)-1)){ #for loop
    s<-c() #initial variable s as empty
    s<-my_data[sample(length(my_data), round(length(my_data)*the_sample_size[i]), replace = FALSE)]#define s as the samples selected from my_data
    for (j in 1:1000){ #for loop
      a[j,i]<-s[sample(length(s),1,replace=FALSE)] #select a sample from s and put it into dataframe a
    }#end 2nd for loop
    mean3[i]<-mean(a[,i]) #put each mean  into mean3
  }#end 1st for loop
  colnames(a)<-c('1%sample','10%sample','25%sample','50%sample','80%sample') #name a's columns 
  a #output a
} #finish the function
data_frame_2(abalone$weight.w) #run data_frame_2() with abalone$weight.w
```

Problem 4
```{r}
#We will define a function grid_histogram_2(), use the function histograms() to create the grid of histograms for all columns in a 
grid_histogram_2<-function(my_data){ #define a function grid_histogram_2() with input my_data
  size4<-c(0.01,0.1,0.25,0.5,0.8) #initial a variable size4 with samplesize which we used for a
  par(mfrow=c(2,3)) #use par() to arrange the histogram in rows and columns, with parameters 2 and 3
  for (i in 1:5){ #for loop
    histograms(data_frame_2(my_data)[,i],size4[i]) #use histograms() to plot histograms for all columns in a 
  } #end for loop
  histograms(my_data,1) #use histograms() to plot histogram for samples
} #finish the function
grid_histogram_2(abalone$weight.w) #run grid_histogram_2() with abalone$weight.w
```

Problem 5
```{r}
#we will create a function data_frame_3 to calculate min, max, mean and variance of each column in dataframe a and the 100% sample
data_frame_3<-function(my_data){ #create function data_frame_3 with input my_data
  resample<-data.frame(c1=c(NA),c2=c(NA),c3=c(NA),c4=c(NA),c5=c(NA)) #initial an empty dataframe resample with 5 columns
  for (i in 1:5){ #use for loop
    resample[1,i]<-min(data_frame_2(my_data)[,i]) #initial min of resample columns
    resample[2,i]<-max(data_frame_2(my_data)[,i]) #initial max of resample columns
    resample[3,i]<-mean(data_frame_2(my_data)[,i]) #initial mean of resample columns
    resample[4,i]<-var(data_frame_2(my_data)[,i]) #initial var of resample columns
  }#end for loop
  q5<-data.frame(resample,Whole_wgt_sample(my_data,1,length(my_data))) #initial dataframe q5 and put resample and 100% sample together in q5
  rownames(q5)=c('ResampleMin', 'ResampleMax', 'ResampleMean', 'ResampleVar')#initial names for q5's rows
  colnames(q5)<-c('1%sample','10%sample','25%sample','50%sample','80%sample','100%sample') #initial names for q5's columns
  q5 #output dataframe q5
}  #finish the function
data_frame_3(abalone$weight.w)#run data_frame_3() with abalone$weight.w
```

Problem 6
```{r}
#we will define a function to create a single histogram of 100% data, and label lines that represent the 1%, 10%, 25%, 50%, and 80% SampleMean
histogram1<-function(my_data){ #define a function histogram1 with input my_data
  par(mfrow=c(1,1)) #use par() to arrange the one single histogram in plots area
  nums<-c(1,10,25,50,80) #initial a variable nums and use it in creating the text for each lines represent the 1%, 10%, 25%, 50%, and 80% SampleMean in histogram
  hist(my_data,main=paste('Histogram with 100% sample'),xlab='variable')#use hist() to create histogram with input my_data, name the title 'Histogram with 100% sample
  for (i in 1:(length(data_frame_1(my_data)[3,])-1)){#for loop
    abline(v=data_frame_1(my_data)[3,i],col=i+2)#draw vertical lines for each samplemean with different color
    mtext(paste('x=',nums[i],'% SampleMean'),at=-0.7+i*0.6,col=i+2)#use mtext to write text x=i% SampleMean for each vertical line with certain color in histogram
  } #end for loop
} #finish the  function
histogram1(abalone$weight.w)#run histogram1() with abalone$weight.w
```

Problem 7
```{r}
#we will define a function to create a single histogram of 100% data and overlay and label lines that represent the 1%, 10%, 25%, 50%, and 80% ResampleMean
histogram2<-function(my_data){ #define function histogram2 with input my_data
  par(mfrow=c(1,1)) #use par() to arrange the one single histogram in plots area
  nums<-c(1,10,25,50,80)#initial a variable nums and use it in creating the xtext for each lines represent the 1%, 10%, 25%, 50%, and 80% resampleMean in histogram
  hist(my_data,main=paste('Histogram with 100% sample'),xlab='variable')#use hist() to create histogram with my_data, and name the title 'Histogram with 100% sample'
  for (i in 1:(length(data_frame_3(my_data)[3,])-1)){#for loop
    abline(v=data_frame_3(my_data)[3,i])#draw vertical line for each resamplemean 
    mtext(paste('x=',nums[i],'% ReSampleMean'),at=-0.7+i*0.7,col=i+2)#use mtext to write text x=i% ReampleMean for each vertical line with certain color in histogram
  }#end for loop
}#finish the function
histogram2(abalone$weight.w)#run histogram2() with abalone$weight.w
```

Problem 8
```{r}
require(ggplot2)
#execute functions on diamonds$carat
data_frame_1(diamonds$carat)
grid_histogram_1(diamonds$carat)
data_frame_2(diamonds$carat)
grid_histogram_2(diamonds$carat)
data_frame_3(diamonds$carat)
histogram1(diamonds$carat)
histogram2(diamonds$carat)
#execute functions on faithful$eruptions
data_frame_1(faithful$eruptions)
grid_histogram_1(faithful$eruptions)
data_frame_2(faithful$eruptions)
grid_histogram_2(faithful$eruptions)
data_frame_3(faithful$eruptions)
histogram1(faithful$eruptions)
histogram2(faithful$eruptions)
```

Problem 9
Based on problem 1-9, I learn that with more samples, I could get results with more accurate information and better distribution related to the real situation. Futhermore, if I use repeat smaples of a given size, the mean of the sample tends to be a real mean for that sample, because the sample size is incresing. Then, the distribution will help us to get better estimations.

